|

### 2020-01-12 inst/manuscript/candidaev_figures.Rmd
Finish responses to reviewer comments
Add Supplementary Data S8.

Modify Figure 5. Fix typo in Supplementary Figure S1.

Add headings to Supplementary Data S6 S7 and S8

```{r figure3Plots, include=FALSE}
# import FungiFun2 GO enrichment results
f3_y_go_table <- process_fungifun("figures/f3_GO_DAY_Y.csv")
f3_b_go_table <- process_fungifun("figures/f3_GO_DAY_B.csv")
f3_a1_go_table <- process_fungifun("figures/f3_GO_ATCC10231.csv")
f3_a9_go_table <- process_fungifun("figures/f3_GO_ATCC90028.csv")

@@

# GO term bar plots
f3_y <- plot_go_bar(f3_y_go_table, c(1:4,6, 23,26:28,30, 42,44:46), f3_pal) + 
  annotate("text", x = 14, y = 65, label = "bold('DAY286 Y')", parse = TRUE) + 
  labs(fill = "GO domain") + 
  theme(legend.text = element_text(size = 10), 
        legend.title = element_text(size = 10))

f3_b <- plot_go_bar(f3_b_go_table, c(1:4,6, 54:57,67, 73,75,77,87), f3_pal) + 
  annotate("text", x = 14, y = 60, label = "bold('DAY286 B')", parse = TRUE)

f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:5, 12,14,17,18,24, 26:29), f3_pal) + 
  annotate("text", x = 14, y = 70, label = "bold('ATCC90028')", parse = TRUE)

f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4,6, 31,33:35,45, 49:52), f3_pal) + 
  annotate("text", x = 14, y = 70, label = "bold('ATCC10231')", parse = TRUE)

@@

```{r figure3, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'),  dev.args=f3_args, dpi=600}
# draw figure 3
ggarrange(f3_y, f3_a9, 
          f3_a1, f3_b, 
          labels = NULL, 
          ncol = 2, 
          nrow = 2, 
          common.legend = TRUE, 
          legend = "bottom", 
          align = "hv")
```

>>>>

```{r figure3Plots, include=FALSE}
# import FungiFun2 GO enrichment results
f3_y_go_table <- process_fungifun("figures/f3_GO_DAY_Y.csv")
f3_y_go_table[43,2] <- "d-p-m-protein mannosyltransferase activity"
f3_b_go_table <- process_fungifun("figures/f3_GO_DAY_B.csv")
f3_a1_go_table <- process_fungifun("figures/f3_GO_ATCC10231.csv")
f3_a9_go_table <- process_fungifun("figures/f3_GO_ATCC90028.csv")

@@

# GO term bar plots
f3_y <- plot_go_bar(f3_y_go_table, c(1:8, 23:30, 42:49), f3_pal) +
  theme(legend.position = "none") + 
  facet_grid(rows = vars(GO.type), scales = "free")

f3_b <- plot_go_bar(f3_b_go_table, c(1:8, 53:60, 73:80), f3_pal) +
  theme(legend.position = "none") + 
  facet_grid(rows = vars(GO.type), scales = "free")

f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:8, 12:19, 26:29), f3_pal) +
  theme(legend.position = "none") + 
  facet_grid(rows = vars(GO.type), scales = "free")

f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:8, 31:38, 48:55), f3_pal) +
  theme(legend.position = "none") + 
  facet_grid(rows = vars(GO.type), scales = "free")

@@

```{r figure3, fig.width=7.2, fig.height=7, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'),  dev.args=f3_args, dpi=600}
# draw figure 3
ggarrange(f3_y, f3_a9, 
          f3_a1, f3_b, 
          labels = c("A", "B", "C", "D"), 
          ncol = 2, 
          nrow = 2, 
          align = "hv")
```

### 2020-01-12 inst/manuscript/candidaev_supplement.Rmd
Finish responses to reviewer comments
Add Supplementary Data S8.

Modify Figure 5. Fix typo in Supplementary Figure S1.

Add headings to Supplementary Data S6 S7 and S8

```{r figureS3, fig.cap=fS3_cap, fig.height=7, fig.width=5.5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS3_args, dpi=600}
fS3_cap <- c("\\textbf{MAIN} Sub.")

@@

## Construct figure S4 components
# Fig S4A = compare DAY286 yeast EV and biofilm EV proteins via venn diagram
fS4_a <- plot_venn(list("DAY286\nYeast EV" = y_ev2, 
                             "DAY286\nBiofilm EV" = b_ev2),
                        use_uniprot = TRUE, type = "plot",
                        fontfamily = "sans",
                        cex = 0.8,
                        cat.fontfamily = "sans",
                        cat.just = list(c(0.5,1.7), c(0.5,1.5)),
                        margin = 0.05) %>% 
  as_ggplot() + 
  theme(plot.margin = unit(c(0,1.5,0,1.5), "cm"))

@@

```{r figureS4, fig.cap=fS4_cap, fig.height=6, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS4_args, dpi=600}
fS4_cap <- c("\\textbf{MAIN} Sub.")

@@

```{r figureS5, fig.cap=fS5_cap, fig.height=7, fig.width=7, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS5_args, dpi=600}
fS5_cap <- c("\\textbf{MAIN} Sub.")

>>>>

```{r figureS3, fig.cap=fS3_cap, fig.height=7, fig.width=5.5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS3_args, dpi=600}
fS3_cap <- c("\\textbf{Statistical comparisons of \\textit{C. albicans} EV 
              isolations.} \\textit{(A)} Boxplot showing EV mode diameter 
              measured using NTA. Differences in average EV mode diameters
              were compared using One-way ANOVA followed by Tukey's HSD 
              \\textit{post-hoc} test. Adjusted p-values indicating 
              significant differences are shown. \\textit{(B)} Boxplot showing 
              total particle concentration for each EV preparation as measured 
              by NTA. Differences in average total particle concentration 
              were compared by Kruskal-Wallis test followed by Dunn's Test.
              Adjusted p-values indicating significant differences are shown.")

@@

## Construct figure S4 components
# Fig S4A = compare DAY286 yeast EV and biofilm EV proteins via venn diagram
fS4_a <- plot_venn(list("DAY286\nYeast EV" = y_ev2, 
                             "DAY286\nBiofilm EV" = b_ev2),
                        use_uniprot = TRUE, type = "plot",
                        fontfamily = "sans",
                        cex = 0.8,
                        cat.fontfamily = "sans",
                        cat.just = list(c(0.5,1.7), c(0.5,1.5)),
                        margin = 0.05) %>% 
  as_ggplot() + 
  theme(plot.margin = unit(c(0,2,0,2), "cm"))

@@

(ref:limma) [@cox2014; @ritchie2015]

```{r figureS4, fig.cap=fS4_cap, fig.height=6, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS4_args, dpi=600}
fS4_cap <- c("\\textbf{Differential abundance analysis of proteins identified 
              in EVs isolated from two different morphologies of the DAY286 
              \\textit{C. albicans} strain.} \\textit{(A)} Venn diagram 
              comparing the biofilm EV and yeast EV proteome data sets shown 
              in Figure 2A. \\textit{(B)} Volcano plot depicting significantly 
              enriched biofilm EV or yeast EV proteins. Differential abundance 
              analysis was performed by comparing the mean normalised LFQ
              intensities of common DAY286 EV proteins (i.e. proteins in the 
              Venn overlap) using the package \\textit{limma} (ref:limma). 
              Significantly enriched proteins were identified using a 
              Benjamini-Hochberg adjusted p-value cut-off of 0.01 and a 
              log\\textsubscript{2}(FC) cut-off of 1. Counts of significant and 
              non-significant proeins are indicated. Proteins with a
              log\\textsubscript{2}(FC) greater than 5 or less than -5 are 
              labelled. Data underlying this plot are provided in 
              Supplementary Data S6.")

@@

(ref:fungifun) [@priebe2015]

```{r figureS5, fig.cap=fS5_cap, fig.height=7, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS5_args, dpi=600}
fS5_cap <- c("\\textbf{Functional enrichment analyses of EVs from two DAY286 
              morphologies.} Top 10 signficantly enriched biological process 
              (BP), cellular component (CC), and molecular function (MF) GO 
              terms for the \\textit{(A)} yeast EV enriched and exclusive proteins or
              \\textit{(B)} biofilm EV enriched or exclusive proteins shown in 
              Supplementary Figure S4. GO analyses were performed using 
              the online tool FungiFun2 (elbe.hki-jena.de/fungifun) 
              (Hypergeometric distribution, Benjamini-Hochberg adjusted 
              p-value < 0.01)
              (ref:fungifun). The GO terms are presented top to bottom in order 
              of increasing adjusted p-value. Full lists of enriched GO terms
              can be found in Supplementary Data S7.")
